20220426_main_plot_t_test

### 2022-04-27 exploratory/20220426_main_plot_t_test.Rmd
made a table for t-tests

```{r setup, include=FALSE}
# load libraries
library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom)

@@

## T-tests
- Independent samples *t*-test between men and women, separate for conditions and experiments
- Output into a large table

```{r t_exp_all}
# t test by groups for exp_all variable
casual_tib %>% 
  unite(homosexual, diff_likelihood, diff_standard,
              col = "condition_hs_lh_sd", sep = "_") %>% 
  pivot_longer(c(m_exp_all, f_exp_all), values_to = "exp_all",
               names_to = "gender", names_pattern = "(.)_exp_all") %>% 
  select(condition_hs_lh_sd, gender, exp_all) %>% 
  nest_by(condition_hs_lh_sd) %>% 
  mutate(t.test(exp_all ~ gender, data = data) %>% tidy()) %>% 
  select(condition_hs_lh_sd, statistic, p.value, parameter) %>% 
  kable()
```

>>>>

```{r setup, include=FALSE}
# load libraries
library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)

@@

## T-tests
- Independent samples *t*-test between men and women, separate for conditions and experiments
- Output into tables with descriptives and test results, separate by variables

```{r t_all_var}
# create a long tibble
casual_long <- 
  casual_tib %>%
  unite(homosexual, diff_likelihood, diff_standard,
        col = "homosexual_dlikelihood_dstandard", sep = "_") %>% 
  pivot_longer(-c(seed, homosexual_dlikelihood_dstandard), 
               names_to = c("gender", ".value"), 
               names_pattern = "(.)_(.*)"
  )

# descriptives
casual_des <- 
  casual_long %>% 
  group_by(homosexual_dlikelihood_dstandard, gender) %>% 
  summarise(across(inpool:partner_ip, 
                   list(mean = mean, sd = sd),
                   .names = "{.col}.{.fn}")) %>% 
  pivot_wider(names_from = gender, 
              values_from = -c(homosexual_dlikelihood_dstandard, gender),
              names_glue = "{gender}_{.value}")

# t test by groups for exp_all variable
casual_t_test <- 
  casual_long %>% 
  nest_by(homosexual_dlikelihood_dstandard) %>% 
  mutate(
    inpool = t.test(inpool ~ gender, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    outpool = t.test(outpool ~ gender, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    exp_all = t.test(exp_all ~ gender, data = data) %>% tidy() %>% 
      # somehow the map function doesn't work here and I wonder why...
      select(statistic, p.value, parameter),
    exp_ip = t.test(exp_ip ~ gender, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    partner_all = t.test(partner_all ~ gender, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    partner_ip = t.test(partner_ip ~ gender, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter)
    ) %>% 
  select(-data) %>% 
  unnest(cols = -homosexual_dlikelihood_dstandard, names_sep = ".")

# effect size
casual_d <- 
  casual_long %>% 
  nest_by(homosexual_dlikelihood_dstandard) %>% 
  mutate(
    inpool.d = cohens_d(inpool ~ gender, data = data) %>% pull(Cohens_d),
    outpool.d = cohens_d(outpool ~ gender, data = data) %>% pull(Cohens_d),
    exp_all.d = cohens_d(exp_all ~ gender, data = data) %>% pull(Cohens_d),
    exp_ip.d = cohens_d(exp_ip ~ gender, data = data) %>% pull(Cohens_d),
    partner_all.d = cohens_d(partner_all ~ gender, data = data) %>% pull(Cohens_d),
    partner_ip.d = cohens_d(partner_ip ~ gender, data = data) %>% pull(Cohens_d)
    )

# combine the descriptives, test results, and effect size
full_join(casual_des, casual_t_test, casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
  kable()
```
